MCC Kids Model Predictions

### 2019-02-11 stats/kids/kids_model_predictions.Rmd
update kids model pred plot

@@

var ex3Data = dataFromR.ex3data
var modelParams = dataFromR.modelParams
var ageConditions = dataFromR.ageConditions

@@

   var ageConditionSpecificData =  _.filter(ex3Data, {age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

@@

@@

}
'
```
```{r noisy combined model predictions}

@@

pred_plot <- ggplot(plot_model_pred)+
  #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(y="Proportion Expected Choice")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  guides(col = F)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()
```

@@

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

## importing data
ex3_data <- read_csv(file="../data/kids_ex3_data.csv")

# files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")
# 
# raw_data <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,42,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data <- bind_rows(raw_data, id)
# }
# 
# raw_data <- raw_data %>%
#   mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
#          subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
#          subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))
# 
# raw_data%>%
#   #group_by(paste(subid,test_date))%>%
#   group_by(subid)%>%
#   summarise(n= n())
#   
# unique(raw_data$subid)
# 
# log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "ex3p")%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# #unique(log$subid)
# sum(log$keep_drop == "drop")
# 
# d <- left_join(raw_data,log, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"),
#          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
#          Alignment = alignment)%>%
#   select(-speaker,-alignment)
# 
# 
# #write_csv(d, "../data/kids_ex3_data.csv")

@@

p_data <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(age_bin = age_num - 3)%>%
  group_by(Speaker, Alignment ,age_bin, subid)

ggplot(model_comp_mean_ci)+
  geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
  geom_line(aes(age_bin, mean, col = model), size = 1, alpha = 1, linetype = 2) + 
  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()

>>>>

kids_model_pred <- model_pred %>%
  mutate(age_bin = age_bin.age_bin)%>%
  select(rsaPredictions_diff_cong,rsaPredictions_diff_incong,rsaPredictions_same_cong,rsaPredictions_same_incong,age_bin)%>%
  gather(condition, prop_informative, -age_bin)%>%
  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
```

@@

var ex3Data = dataFromR.ex3data
var modelParams = dataFromR.modelParams[0]
var ageConditions = dataFromR.ageConditions

@@

   var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

   var ageSpecificParams =  _.filter(modelParams, {age_bin: conditionInfo.age_bin})

    display(JSON.stringify(ageSpecificParams))

    var speakerOptimality = ageSpecificParams.so_map

    var diff_priorReg = ageSpecificParams.diff_priorReg_map

@@

}
'
```

@@

}
'
```

```{r noisy combined model predictions}

@@

ggplot(kids_model_pred)+
  #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
  geom_line(aes(age_bin, prop_informative), col = "black", size = 0.4, alpha = 1) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(y="Proportion Expected Choice")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  guides(col = F)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()
```

@@

@@

p_data <- ex3_data %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(age_bin = age_num - 3)%>%
  group_by(Speaker, Alignment ,age_bin, subid)

ggplot(kids_model_pred)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
  geom_line(aes(age_bin, prop_informative, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()
